Progress Report

### 2020-07-28 documentation/Optimization Work/07_24_20.tex
adding notes on progress report for reviewing methods of phase optimization

\section{Next Steps: Methods for Phase Optimization}
\begin{enumerate}
\item
	Method from \cite{huang2018achievable}.
\begin{itemize}
\item
	No LOS of correlation
\item
	Requires full CSIT at IRS
\item 
	Assumes a ZF precoder in order to simplify sum-capacity objective function.
\item
	Alternating algorithm approach with two main steps
	\begin{enumerate}
	\item 
		Minimize transmission power w.r.t phases
	\item
		Maximize rate wrt power
	\end{enumerate}
\end{itemize}

\item 
	Method from \cite{huang2018achievable}.

>>>>

\section{Next Steps: Methods for Phase Optimization}
\begin{enumerate}
\item
	Method from \cite{huang2018achievable}.
\begin{itemize}
\item
	No LOS or correlation considered in system model.
\item
	Algorithm requires full CSIT at IRS
\item 
	Assumes a ZF precoder in order to simplify sum-capacity objective function.
\item
	Alternating algorithm approach with two main steps
	\begin{enumerate}
	\item 
		Minimize transmission power w.r.t phases
	\item
		Maximize rate wrt power
	\end{enumerate}
\end{itemize}

\item 
	Method from \cite{kammoun2020asymptotic}.
	\begin{itemize}
		\item 
			Algorithm only requires channel statistics for the RIS update
		\item
			System model includes correlation.
		\item
			Does transmitter need perfect CSI or can they make do with just knowing the composite channel.
		\item
			Uses max-min SINR as objective
		\item
			Optimizes the beamformer, the powers and RIS (continuous phases allowed)
		\item
			Question: \cite[Section III ]{kammoun2020asymptotic} makes a claim that for a single rank channel the RIS only offers a "substantial" benefit if there
			is a single user.  This makes sense for a Decision-Feedback equalization sense but it is still not clear to me why the benefit
	\end{itemize}
